Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-26 latex/article.tex
typos

   \end{center}
   \caption{\emph{Left column}: Mean curvature, first and second principal directions and normales estimation on Snow Microstructures with a digital domain of $233^3$ and a radius of 8. 
  \emph{Right column:} Mean curvature, first and second principal directions and normales estimantion on XYZ Dragon with a digital domain of $510^3$ and a radius of 8.}
   \label{fig:adaptive}
   \vspace{-0.35cm}
 \end{figure}

>>>>

   \end{center}
   \caption{\emph{Left column}: Mean curvature, first and second
     principal directions and normal vector field estimation on Snow Microstructures ($233^3$ and  $R=8$). 
  \emph{Right column:} Mean curvature, first and second principal
  directions and normal vector field estimantion on XYZ Dragon($510^3$
  and $R=8$). Normal vectors are colored with a mapping their
  component to RGB color space.}
   \label{fig:adaptive}
   \vspace{-0.35cm}
 \end{figure}
